The Impact of Subway Systems on Air Pollution

### 2023-02-24 Paper Two .qmd
Add two tabes (China and Chile

```{r,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: tab-one
library(here)
library(dplyr)
library(knitr)
subway_data_raw <- read.csv(file = '/Users/lucas/Documents/paper2/Subway_Ridership_V4.csv')
#subway_data_raw <- read.csv(file = '/Users/xiuzh/Desktop/readingcourse/paper2/Subway_Ridership_V4.csv')

@@

## 3.2 Subway in Chile
In Table 2, the table includes information on Valparaiso, Chile's public transit system ridership, among other things. The data provides information on the total number of ridership for each year but not the particular months or quarters during which the ridership was logged. Annually is the reference time.

@@

new <- subway_data_monthly%>%group_by(Country)%>%summarise(Total=sum(as.numeric(Ridership),na.rm=T))%>%filter(Country=="Chile")

kable(head(subway_data_monthly,5), caption = "Subway City in Chile (First 5 rows)")
```

## 3.3 PM10 across Countries

@@

In Table 3, the inauguration and construction times of various cities, as well as the plan year and an unnamed variable X, are listed in Table 3. Each community's unnamed infrastructure project is the subject of the material. The infrastructure project's completion year is indicated by the opening date, while the development phase's initial start year is indicated by the beginning building date. The project's original approach was developed during the plan year.

```{r,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: Tab-three
library(knitr)
kable(head(new_subway_city,10), caption = "Subway_City (First 5 rows)")
```

>>>>

```{r,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: tab-one
library(here)
library(dplyr)
library(knitr)
#subway_data_raw <- read.csv(file = '/Users/lucas/Documents/paper2/Subway_Ridership_V4.csv')
subway_data_raw <- read.csv(file = '/Users/xiuzh/Desktop/readingcourse/paper2/Subway_Ridership_V4.csv')

@@

## 3.2 Subway in Chile
In Table 2, the table includes information on Valparaiso, Chile's public transit system ridership, among other things. The data provides information on the total number of ridership for each year but not the particular months or quarters during which the ridership was logged. Annually is the reference time. This table is an analysis of Subway's annual ridership data in Chile from 2005 to 2009. After filtering the data to only include records for Chile, the new data is converted the Ridership column to a numeric format by removing commas. The table indicates the total ridership for each year in Chile. It is clear to see that the annual ridership increae each year. Especially in 2005-2006, the ridership increase more than 7,000,000.

@@

new <- subway_data_monthly%>%filter(Country=="Chile")
#new$Ridership<-as.numeric(new$Ridership)
new$Ridership <- as.numeric(gsub(",", "", new$Ridership))

mytable<-new%>%group_by(Country,Year)%>%summarise(`Total Ridership`=sum(Ridership))

kable(mytable, caption = "Annaul Ridership in Chile (2005-2009)")
```

In comparison to Table 1, Table 2 is the annual ridership in China from 2005 to 2019. As a result, the ridership in China also shows an increasing pattern since 2005. However, there is a sharpe decresae from 2016 to 2017 in terms of the Ridership and it gradually increase back to the orginal level. Since China is a country with large population, the ridership are generally higher than the one in Chile.

```{r,fig.width= 15,fig.height= 20,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: Tab-three
library(here)
library(dplyr)

new <- subway_data_monthly%>%filter(Country=="China")
#new$Ridership<-as.numeric(new$Ridership)
new$Ridership <- as.numeric(gsub(",", "", new$Ridership))

mytable<-new%>%group_by(Country,Year)%>%summarise(`Total Ridership`=sum(Ridership))

kable(mytable, caption = "Annaul Ridership in China (2005-2019)")
```

## 3.3 PM10 in Different Countries

@@

In Table 4, the inauguration and construction times of various cities, as well as the plan year and an unnamed variable X, are listed in Table 4. Each community's unnamed infrastructure project is the subject of the material. The infrastructure project's completion year is indicated by the opening date, while the development phase's initial start year is indicated by the beginning building date. The project's original approach was developed during the plan year.

```{r,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: Tab-four
library(knitr)
kable(head(new_subway_city,10), caption = "Subway_City (First 5 rows)")
```
